---
title: "filter_polygon"
author: "JT_Miller"
date: "6/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# started by Katja Seltmann, 2020
# Script to map occurrence records of species (lat/long) that occur only within the boundaries of Coal Oil Point Reserve (shp file)
# COPR occurrence records in tab-delimited format: https://ucsb.box.com/s/7xp88xhg1xn7decsv0t3ll8du653deub
# COPR boundary files: https://ucsb.box.com/s/nd1s0e3ted8zsu0ir4wbxu7qpe94ht8o

#The goal of this script is to:
#draw boundary of copr on map
#Trim specimen_data (occurrence.txt) based on copr boundary creating new file that only contains specimens whose coordinates are within that boundary

```{r}
#required libraries
library(ggplot2)
library(maptools)
library(sf)
library(maps)
library(raster)
library(rgdal)
library(dplyr)
library(MapGAM)
library(tidyr)
library(plotly)
```


```{r}
#file that contains over 75K of specimen data with lat/long coordinates
specimen_data <- read.delim(file="occurrence.txt",header=TRUE)
```


```{r}
#print data dimensions
dim(specimen_data)

names(specimen_data)

```

```{r}
#remove rows where lat/long do not exist
specimen_data <- subset(specimen_data, !is.na(order) & !is.na(decimalLongitude) & !is.na(decimalLatitude))


```


```{r}
#print data dimensions
dim(specimen_data)


```


```{r}
#remove columns and rows for smaller test dataset that only includes long and lat, and limit to only 100 rows for testing

#column decimalLongitude = 134
#column decimalLatitude = 133

specimen_data_less <-specimen_data[1:100,c(134,133)]
head(specimen_data_less)



#This was just running through the data columns to make sure there wasnt an established CRS labeled in the columns
specimen_crs <- specimen_data %>% 
  dplyr::select(decimalLatitude, decimalLongitude, coordinateUncertaintyInMeters )
```


```{r}
#print dimensions of new dataset
dim(specimen_data_less)

```

```{r}
#read boundary from shp file
copr_boundary_2020 <- st_read("COPR_Boundary_2010/COPR_boundary2010.shp") #Vector type. 

copr_boundary_2020
#What is the projection of copr_boundary_2020

#Global datum is NAD83. California zone 5 is code: ESPG:2229. 

st_geometry_type(copr_boundary_2020) #18 levels, MultiPolygon

st_crs(copr_boundary_2020) #Projection is lcc...not sure what this is: https://en.wikipedia.org/wiki/Lambert_conformal_conic_projection 

#so this is in lat long, but not decimal formatting (degrees)

extent(copr_boundary_2020) 

st_bbox(copr_boundary_2020) #Same thing as above just easier formatting on the boundary edges. 

head(copr_boundary_2020)
#Seems there is only one feature, therefore we can't split it up in any meaningful way to look at individual parts. 

copr_boundary_2020
```



```{r}
#draw boundary from shp file
ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black")


```
```{r}
#Technically the ESPG:4269 (NAD83) and ESPG:4326 (WGS84) are not equivalent, for most applications they can treated as equivalent. 

#First lets change the txt. data into a sf object that uses the standard crs = 4326 for latlong. 

occur_sf_orig <- st_as_sf(specimen_data_less, coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326)

#Now lets transform this new sf object to the crs using our boundary data 

occur_sf_new <- st_transform(occur_sf_orig, 
                             st_crs(copr_boundary_2020))
#Check the extents, they appear to be in the same range 
extent(occur_sf_new)

extent(copr_boundary_2020)
```

```{r}

#Plotting shows that the data points do appear in the right location now! We are not getting a display of the map however, lets see if we can troubleshoot this. 

#Edit: It actually appears that the map is on there Just REALLY small, Zooming in on this will help clear this up. 
ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occur_sf_new, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")
```
```{r}
#Lets crop the map

extent(copr_boundary_2020)

occur_cropped <- st_crop(occur_sf_new, xmin = 5993354, xmax = 5996966,
                                      ymin = 1975712, ymax = 1979692)

ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occur_cropped, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")

#Look at data, plotting on a google map to see 

#ANNNNND Theres only one data point on it....thats rather anticlimatic....
  
```

```{r}
#Lets try expanding the dataset to make sure theres more specimen that show up?
specimen_data_more <-specimen_data[1:1000,c(134,133)]

#First lets change the txt. data into a sf object that uses the standard crs = 4326 for latlong. 

occur_sf_orig_more <- st_as_sf(specimen_data_more, coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326)

#Now lets transform this new sf object to the crs using our boundary data 

occur_sf_new_more <- st_transform(occur_sf_orig_more, 
                             st_crs(copr_boundary_2020))
#Check the extents, they appear to be in the same range 
extent(occur_sf_new_more)

extent(copr_boundary_2020)


```

```{r}
occur_cropped_more <- st_crop(occur_sf_new_more, xmin = 5993354, xmax = 5996966,
                                      ymin = 1975712, ymax = 1979692)

ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occur_cropped_more, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")

```

```{r}
#Lets try all of it?
specimen_data_all <-specimen_data[c(134,133)]

```

```{r}

#First lets change the txt. data into a sf object that uses the standard crs = 4326 for latlong. 

occur_sf_orig_all <- st_as_sf(specimen_data_all, coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326)

#Now lets transform this new sf object to the crs using our boundary data 

occur_sf_new_all <- st_transform(occur_sf_orig_all, 
                             st_crs(copr_boundary_2020))
#Check the extents, they appear to be in the same range 
extent(occur_sf_new_all)

copr_boundary_extent <- extent(copr_boundary_2020) 


```

```{r}
occur_cropped_all <- st_crop(occur_sf_new_all, xmin = 5993354, xmax = 5996966,
                                                 ymin = 1975712, ymax = 1979692)

ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occur_cropped_all, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")

```



















```{r}

#Lets try the st_within function on the 100 sample data set in order to see if there should only be one true output
occur_data_within_polygon_small <- st_within(occur_sf_new, copr_boundary_2020, sparse = FALSE) 

occur_data_within_polygon_small #Success! there is only one TRUE 


#So we can get the return of false and TRUE values for what is actually inside the polygon. Now we just need to find a way to associate the TRUE/FALSE outputs with their parent values and then subset a dataset with only TRUE outputs. 


```






```{r}
#Using subset feature I found online for trimming data to just whats inside the vector. 

occurence_subset <- occur_sf_new[copr_boundary_2020,] #It worked!!!
```

```{r}
ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occurence_subset, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")


```

```{r}
#Now with the larger dataset 

occurence_all_subset <- occur_sf_new_all[copr_boundary_2020,] #Notice that there is 1603 observations, however many of these are repeated. 
```


```{r}
ggplot() +
  geom_sf(data = copr_boundary_2020, fill = "palegreen", color = "black") +
  geom_sf(occurence_all_subset, mapping = aes(geometry = geometry), size = 1) +
  ggtitle("Occurence of Plant Specimens within Coal Oil Point")

```



```{r}
#This is looking if we can associate the order with the data points for some clarity in what we are looking at 

specimen_data_order <- specimen_data[c(134, 133, 194)]
```



```{r}

#First lets change the txt. data into a sf object that uses the standard crs = 4326 for latlong. 

occur_sf_order <- st_as_sf(specimen_data_order, coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326)

#Now lets transform this new sf object to the crs using our boundary data 

occur_sf_order_new <- st_transform(occur_sf_order, 
                             st_crs(copr_boundary_2020))
#Check the extents, they appear to be in the same range 
extent(occur_sf_order_new)

extent(copr_boundary_2020)
```
```{r}
#Now lets subset 

occur_sf_order_new_subset <- occur_sf_order_new[copr_boundary_2020,]
```

```{r}
##Export as a csv file

directory <- getwd()
directory

write.csv(occur_sf_order_new_subset, "C:/Users/JTroo/Desktop/Github/occurence_maps/occurrence-maps/filter_polygon/occur.csv", row.names = TRUE)
 #So this is the exported dataframe for just taxonomy and geo coordinates. 
```







```{r}

#Now lets get the whole data set into its own csv


#First lets change the txt. data into a sf object that uses the standard crs = 4326 for latlong. 

#Note: The crs 4326 is referring to the ESPG code WGS84 which is the standard world wide latlong GIS data format that is used for global spatial data. A common user of WGS84 is Google Earth. The specific CRS of the boundary data, NAD83 is considered old fashioned since it is specifically referring to a specified location. 

occur_sf_full <- st_as_sf(specimen_data, coords = c('decimalLongitude', 'decimalLatitude'), crs = 4326)

#Now lets transform this new sf object to the crs using our boundary data 

occur_sf_full_new <- st_transform(occur_sf_full, 
                             st_crs(copr_boundary_2020))
#Check the extents, they appear to be in the same range 
extent(occur_sf_full_new)

extent(copr_boundary_2020)
```

```{r}
#Now lets subset 

occur_sf_full_new_subset <- occur_sf_full_new[copr_boundary_2020,]
```

```{r}
##Export as a csv file


write.csv(occur_sf_full_new_subset, "C:/Users/JTroo/Desktop/Github/occurence_maps/occurrence-maps/filter_polygon/occur_full.csv", row.names = TRUE)
 #So this is the exported dataframe with all of the original data included.  
```



















#From here on Im just messing around. 
```{r}
sapply(occur_sf_order_new_subset, function(x) length(unique(x)))

occur_sf_order_new_subset$order

order_colors <- c("blue", "red", "green", "orange",  "purple",  "black",  "gray", "aquamarine", "chartreuse", "brown", "cyan", "goldenrod", "deeppink", "maroon", "seagreen1", "tan1", "slategrey", "tomato")
```
```{r}
df_uniq <- unique(occur_sf_order_new_subset$geometry)

length(df_uniq)
```


  
```{r}
#Now lets graph by order.  

Order_Plot <- ggplot() +
                geom_sf(data = copr_boundary_2020, fill = "grey", color = "black") +
                geom_sf(occur_sf_order_new_subset, mapping = aes(geometry = geometry, color = order,)) +
                ggtitle("Distribution of identified organisms within Coal Oil Point") +
                labs( x = "Longitude", y = "Latitude") +
                theme_gray() +
                theme(legend.key.size = unit(0.5, "cm"), 
                axis.text = element_text(size = 7), 
                )

Order_Plot
```


```{r}
#Making an interactive map, where when you hover over each data point you may see the Taxonomic Order of the observed specimen. 
ggplotly(Order_Plot)

#Heat Map figure out how to make one.

#Well we can make a hover map, however I think the end goal for this would be I want to show the number of observations at each given data point to show how many times that order was observed in that location. There are 98 unique observations while there is 1603 observations therefore there should be a large number of overlap. 
```

```{r}
#Lets try creating a column that assigns values for each observation

occur_count_unique <- occur_sf_order_new_subset %>% group_by(order) %>% mutate(Count = n_distinct(geometry))
```





```{r}
occur_count_unique

fig <- ggplotly(
  ggplot(data = copr_boundary_2020, fill = "grey", color = "black")) +
    geom_sf(occur_count_unique, mapping = aes(geometry = geometry))
)

fig
```

```{r}
#Now lets graph by order.  

Order_Plot2 <- ggplot() +
                geom_sf(data = copr_boundary_2020, fill = "grey", color = "black") + 
  
                geom_sf(occur_count_unique, mapping = aes(geometry = geometry, color = order,)) +
 geom_bin2d() +
                ggtitle("Distribution of identified organisms within Coal Oil Point") +
                labs( x = "Longitude", y = "Latitude", fill = "# of Observations") +
                theme_gray() +
                theme(legend.key.size = unit(0.5, "cm"), 
                axis.text = element_text(size = 7), 
                )

Order_Plot2

ggplotly(Order_Plot2)
```


```{r}
#Seems we need to seperate out the geometry column into new columns 


occurence_order_subset_sep <- occur_sf_order_new_subset %>%
  dplyr::mutate(lat = sf::st_coordinates(.)[,1],
                lon = sf::st_coordinates(.)[,2])
occurence_all_subset_sep
```


```{r}
#Make a second df of unique counts for each order using this newly adjusted separation df

#occurence_order_subset_sep_unique <- occurence_order_subset_sep %>% group_by(order) %>% mutate(Count = n_distinct(geometry))

#Alright, now we have an x and y column to input into plotly as well as count column. EDIT RETURNS WRONG INFO

```

```{r}
#This is the correct way to sum up counts of the observations per coordinate point
occurence_order_subset_sep_unique <- occurence_order_subset_sep %>% 
  dplyr::group_by(lat, lon) %>% 
  dplyr::mutate(count = n())
```



```{r}
#Now lets graph by order.  

Order_Plot2 <- ggplot() +
                geom_sf(data = copr_boundary_2020, fill = "grey", color = "black") +
                geom_sf(occurence_order_subset_sep_unique, mapping = aes(geometry = geometry, color = order,)) +
  geom_bin2d(occurence_order_subset_sep_unique, mapping = aes(x = lat, y = lon)) +
  facet_wrap(~order)
                

Order_Plot2
```
```{r}
ggplotly(Order_Plot2)
```

  
```{r}
#Now lets graph by order.  

Order_Plot4 <- ggplot() +
                geom_sf(data = copr_boundary_2020, fill = "grey", color = "black") +
                geom_sf(occurence_order_subset_sep_unique, mapping = aes(geometry = geometry,color = order, count = count)) +
                ggtitle("Distribution of identified organisms within Coal Oil Point") +
                labs( x = "Longitude", y = "Latitude") +
                theme_gray() +
                theme(legend.key.size = unit(0.5, "cm"), 
                axis.text = element_text(size = 7), 
                )

ggplotly(Order_Plot4, tooltip = c("order", "count"))
```












  






  




  



