---
title: "Polygon_presentation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# started by Katja Seltmann, 2020
# Script to map occurrence records of species (lat/long) that occur only within the boundaries of Coal Oil Point Reserve (shp file)
# COPR occurrence records in tab-delimited format: https://ucsb.box.com/s/7xp88xhg1xn7decsv0t3ll8du653deub
# COPR boundary files: https://ucsb.box.com/s/nd1s0e3ted8zsu0ir4wbxu7qpe94ht8o

#The goal of this script is to:
#draw boundary of copr on map
#Trim specimen_data (occurrence.txt) based on copr boundary creating new file that only contains specimens whose coordinates are within that boundary

```{r}
#required libraries
library(ggplot2) #library for visualization and plotting.
library(sf) #Spatial objects package, very useful for vector data types
library(raster) #Spatial object package for raster type data
library(rgdal) #Spatial objects
library(dplyr) #Cleaning and data wrangling 
library(tidyr) #Very large package for data organization
library(plotly) #Makes ggplots interactive 
library(tmap) #Another interactive map package
```